### 2016-07-12 conclusions.tex
Only appendix remaining!

\label{sec:conclusions}
Obsersving the expectation of the \ac{IoT} and lack for a low-cost, easy to configure testbed that enable reproducible results for mechanisms to address problems in this area, we provide a in-depth description of the new Aalborg University's \ac{Raspi} testbed for network coding evaluation and how to guarantee replicability and scaling managing of the system. The description shows how to set up interconnected \ac{Raspi}s with small SD cards for local storage, a Raspberry distro image, network connectivity and proper system administration privileges. The exposed work will permit researchers to replicate setups and scenarios for evaluating their strategies in a rapid and manageable way. Future work in the use of \ac{Raspi} devices will focus on expanding the setup and automation of tasks to run the testbed, configure specified network topologies (e.g., with specific connectivity or packet loss ratios), reserve the use of these sub-networks for running tailored experiments and opening the use of the testbed beyond our team at Aalborg University.

>>>>

\label{sec:conclusions}
Observing the expectation of the \ac{IoT} and lack for a low-cost, easy to configure testbed that enables reproducible results for mechanisms to address problems in this area, we provide a in-depth description of the new Aalborg University's \ac{Raspi} testbed for network coding evaluation and how to guarantee replicability and scaling managing of this system. The description shows how to set up interconnected \ac{Raspi}s with small SD cards for local storage, a Raspberry distro image, network connectivity and proper system administration privileges. The exposed work will permit researchers to replicate setups and scenarios for evaluating their strategies in a rapid and manageable way. Future work in the use of \ac{Raspi} devices will focus on expanding the setup and automation of tasks to run the testbed, configure specified network topologies (e.g., with specific connectivity or packet loss ratios), reserve the use of these sub-networks for running tailored experiments and opening the use of the testbed beyond our team at Aalborg University.

### 2016-07-12 cross_compilation.tex
Only appendix remaining!

Configure Kodo to build executables for the \ac{ARM} architecture using
the \ac{Raspi} toolchain:
\begin{lstlisting}[]
$ python waf configure --cxx_mkspec=cxx_raspberry_gxx49_arm
...
'configure' finished successfully (X.XXXs)
\end{lstlisting}
\FloatBarrier
\vspace{-5mm}

Build executables:
\begin{lstlisting}[]
$ python waf build --run_tests
...
'build' finished successfully (2m22.918s)
\end{lstlisting}
\FloatBarrier
\vspace{-5mm}

Make shared library:
\begin{lstlisting}[]
$ python waf install --install_shared_libs --install_path="./shared_test"
\end{lstlisting}
\FloatBarrier
\vspace{-5mm}

Copy shared library to a \ac{Raspi}'s home directory (Alternatively, Kodo can also generate static libraries):
\begin{lstlisting}[]
$ scp -r shared_test/include shared_test/libkodoc.so pi@<RASP_IP>:~/
\end{lstlisting}
\FloatBarrier
\vspace{-5mm}

Copy a binary using Kodo shared library to the \ac{Raspi}'s home directory:
\begin{lstlisting}[]
$ scp -r shared_test/encode_decode_simple pi@<RASP_IP>:~/
\end{lstlisting}
\FloatBarrier
\vspace{-5mm}

Execute binary:
\begin{lstlisting}[]
$ ssh pi@<RASP_IP> ./encode_decode_simple
Data decoded correctly
\end{lstlisting}
\FloatBarrier
\vspace{-5mm}

Cross compiling Kodo applications works provided that above command
returned "Data decoded correctly".

%\item Navigate to the repository and configure \texttt{waf} by typing:
%\texttt{python config.py} and select the 16th ``make specification'' file
%for the \ac{Raspi}, e.g. option \texttt{[16]cxx\_raspberry\_gxx49\_arm}
%presented by the file.
%
%This command configures \texttt{waf} to use the proper compiler and its
%required flags to generate the binaries for the \ac{Raspi}. If the
%configuration was correct, the output will indicate:
%\texttt{'configure' finished successfully (X.XXXs)}, where \texttt{X.XXX}
%is total time in seconds for configuring the project in the server. \\
%
%\item Execute \texttt{python waf build}. If the build process was
%successful, the generated binaries for the \ac{Raspi} should be located
%in \texttt{build/cxx\_raspberry\_gxx49\_arm} in the Kodo repository.
%\textbf{Indicate how the binary files should look like}.
%
%Once this procedure is made, the testbed administrator can relocate the
%generated binary files to the \ac{Raspi}s through the network as desired
%by using the \texttt{scp} command during the configuration step.

%\subsection{Kodo Builds for the \ac{Raspi}, Platform Support and Documentation \textcolor{red}{(WHAT IS THE PURPOSE OF THIS SUBSECTION?)}}
%
%You can check the build status of Kodo, Fifi and other relevant projects
%through their respective repository master branch on our buildbot page
%\cite{steinwurf2016buildbot}. Our buildbot displays the status of the builds
%for Raspbian 8 and GCC 4.9 for the ARM architecture which is the relevant one
%for the \ac{Raspi}. At the link, you can check build status and build
%statistics. Also, documentation about Kodo basics with a tutorial is available
%at \cite{kododocs}.

%\subsection{Kodo python}
%
%Often when simplicity and fast prototyping is of higher importance than speed
%it is often desired to use a scripting language rather than the often faster
%compiled language. Kodo-python provides roughly similar bindings to the
%underlying C++11 implementation of Kodo as Kodo-cpp does. This means that
%python calls to Kodo-python are actually executed in the underlying C++11
%compilied code.
%
%Parsing calls and variables between Python and C++ compiled code is
%not free, but this small introduced overhead may in many cases be worth
%it to take advantage of Pythons and other scripting languages many
%benefits.
%
%Below is a short procedure to use Kodo-python in a \ac{Raspi}.
%
%One advantage of Python compared to Kodo-cpp is that only the Kodo-python
%library needs to be cross compiled. The python scripts using the Kodo
%library needs not to be cross compiled but simply copied to the same
%directory as .
%
%Kodo-python is available at \url{https://github.com/steinwurf/kodo-python}.
%
%
%
%\begin{lstlisting}[]
%$ apt-get update
%$ apt-get install python build-essential libpython-dev python-dev
%\end{lstlisting}
%\FloatBarrier
%\vspace{-5mm}
%  % IN ARCH LINUX, MOD_PYTHON NEEDS TO BE INSTALLED
%
%
%Create a directory to hold our code:
%\begin{lstlisting}[]
%$ CODEDIR="${HOME}/code"
%$ mkdir -p ${CODEDIR}
%$ cd ${CODEDIR}
%\end{lstlisting}
%\FloatBarrier
%\vspace{-5mm}
%
%\begin{lstlisting}[]
%$ git clone git@github.com:steinwurf/kodo-python.git
%\end{lstlisting}
%\FloatBarrier
%\vspace{-5mm}
%
%\begin{lstlisting}[]
%$ cd kodo-python
%$ python2.7 waf configure --cxx_mkspec=cxx_raspberry_gxx49_arm
%$ python waf build
%\end{lstlisting}
%\FloatBarrier
%\vspace{-5mm}
%
%KODO-PYTHON IS NOT WORKING!! WAITING FOR HELP ON STEINWURF DEV.
%
%WRITE HOW TO RUN A KODO PYTHON SCRIPT IN THE RASPIS

>>>>

We first configure \texttt{kodo-cpp} to build executables for the
\ac{ARM} architecture using the \ac{Raspi} toolchain and later build them
by running:
\begin{lstlisting}[]
$ python waf configure --cxx_mkspec=cxx_raspberry_gxx49_arm
...
'configure' finished successfully (X.XXXs)
$ python waf build
...
'build' finished successfully (XmXX.XXs)
\end{lstlisting}
\FloatBarrier
\vspace{-5mm}

If the configuration and build steps are successful, the binaries should
have been created. To be able to use them, we need to create a shared library
that we will use in the \ac{Raspi}. To do this, we run the following command:

\begin{lstlisting}[]
$ python waf install --install_shared_libs --install_path="./shared_test"
...
'install' finished successfully (X.XXXs)
\end{lstlisting}
\FloatBarrier
\vspace{-5mm}

Now, we copy the shared library, binary files and related headers to the
\ac{Raspi} home directory as follows:

\begin{lstlisting}[]
$ scp -r shared_test/include shared_test/libkodoc.so pi@<RASP_IP>:~/
\end{lstlisting}
\FloatBarrier
\vspace{-5mm}

Alternatively and for the testbed administrator reference, Kodo can also
generate static libraries. We log in to the \ac{Raspi} and execute the unit
tests and one of the binaries by running:

\begin{lstlisting}[]
$ ssh pi@<RASP_IP>
$ ./kodocpp_tests
...
[----------] Global test environment tear-down
[==========] 17 tests from 15 test cases ran. (XXXX ms total)
[  PASSED  ] 17 tests.
$ ./encode_decode_simple
Data decoded correctly
\end{lstlisting}
\FloatBarrier
\vspace{-5mm}

If the Kodo cross-compilation worked properly, both the unit tests and
binary run should provide the shown outputs.

%\subsection{Kodo python}
%
%Often when simplicity and fast prototyping is of higher importance than speed
%it is often desired to use a scripting language rather than the often faster
%compiled language. Kodo-python provides roughly similar bindings to the
%underlying C++11 implementation of Kodo as Kodo-cpp does. This means that
%python calls to Kodo-python are actually executed in the underlying C++11
%compilied code.
%
%Parsing calls and variables between Python and C++ compiled code is
%not free, but this small introduced overhead may in many cases be worth
%it to take advantage of Pythons and other scripting languages many
%benefits.
%
%Below is a short procedure to use Kodo-python in a \ac{Raspi}.
%
%One advantage of Python compared to Kodo-cpp is that only the Kodo-python
%library needs to be cross compiled. The python scripts using the Kodo
%library needs not to be cross compiled but simply copied to the same
%directory as .
%
%Kodo-python is available at \url{https://github.com/steinwurf/kodo-python}.
%\begin{lstlisting}[]
%$ apt-get update
%$ apt-get install python build-essential libpython-dev python-dev
%\end{lstlisting}
%\FloatBarrier
%\vspace{-5mm}
%  % IN ARCH LINUX, MOD_PYTHON NEEDS TO BE INSTALLED
%
%
%Create a directory to hold our code:
%\begin{lstlisting}[]
%$ CODEDIR="${HOME}/code"
%$ mkdir -p ${CODEDIR}
%$ cd ${CODEDIR}
%\end{lstlisting}
%\FloatBarrier
%\vspace{-5mm}
%
%\begin{lstlisting}[]
%$ git clone git@github.com:steinwurf/kodo-python.git
%\end{lstlisting}
%\FloatBarrier
%\vspace{-5mm}
%
%\begin{lstlisting}[]
%$ cd kodo-python
%$ python2.7 waf configure --cxx_mkspec=cxx_raspberry_gxx49_arm
%$ python waf build
%\end{lstlisting}
%\FloatBarrier
%\vspace{-5mm}
%
%KODO-PYTHON IS NOT WORKING!! WAITING FOR HELP ON STEINWURF DEV.
%
%WRITE HOW TO RUN A KODO PYTHON SCRIPT IN THE RASPIS
